Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-05-14 mtjournal.tex
changes from Matt.

As discussed in section~\ref{sec:intro}, the TER Plus (TERp) research
tools \cite{snover09terp} provide an optimizer for weighting multiple
simple subscores, including selecting weights for the TER basic
operations. TERp's feature list extends TER to additionally include
synonym tables and an empirically-derived paraphrase table.

%% MO: important to describe basic model before listing features.
TO DO: TERp optimizer [Matt, a brief description here]

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this feature set includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$ decompositions.
  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % MO  (to Matt): is this basic TER or basic TERp?
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase
  table (4 features) % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref).
  % MO: out of curiosity, why do you need 2 features?
  We assign two features here to let the system separately penalize
  ``too short'' translations and ``too long''.
\end{description}

>>>>

As discussed in section~\ref{sec:intro}, the TER Plus (TERp) research
tools \cite{snover09terp} provide an optimizer for weighting multiple
simple subscores, including selecting weights for the TER basic
operations. TERp's feature list extends TER to additionally include
synonymy, stemming, and automatically-derived paraphrases.

%% MO: important to describe basic model before listing features.
The TERp optimizer performs a hill-climbing search, with randomized
restarts, to maximize the correlation of a linear combination of the
features with a set of human judgments.  Within the TERp framework the
features are the count of the various edit types normalized for the
length of the reference so that the dot product of the features with a
vector of edit costs will give the TERp score for a given segment.  In
these experiments, we follow~\inlinecite{snover09terp} by first
aligning the MT outputs with the reference, using TERp with a set of
default edit costs, to find the counts of the various edit types.
These alignments and edit costs are then held constant to optimize the
edit costs. In the case of comparing TERp without the paraphrasing
feature, a separate alignment was performed without that feature
enabled.  Additional features can be added to the TERp optimization
framework and optimized in the same manner as the edit costs.

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this feature set includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$ decompositions.
  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, excluding paraphrases, which include a separate cost
  for each of matches, insertions, deletions, substitutions, shifts, and
  synonym matches and stem matches. The \textbf{T} set includes 7 features.
\item[P]: features from the automatically-derived TERp paraphrase
  table. These are four features which are a function of of the edit
  distance between the two phrases in each paraphrase and the
  probability of the paraphrase.
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref).
  % MO: out of curiosity, why do you need 2 features?
  We assign two features here to let the system separately penalize
  ``too short'' translations and ``too long''.
\end{description}
